TG2 Publications

### 2025-08-18 papers.qmd
minor edit, 250812GH
Added short sentence describing why the books are relevant

* Harrell FE. Regression Modeling Strategies: With Applications to Linear Models, Logistic Regression, and Survival Analysis. Springer: New York, 2015.

* Royston P, Sauerbrei W. Multivariable model-building: a pragmatic approach to regression analysis based on fractional polynomials for modelling continuous variables. John Wiley & Sons; 2008.

* Wood S. Generalized Additive Models. Chapman & Hall/CRC: New York, 2006.

* Miller A. Subset Selection in Regression. Taylor & Francis: Boca Raton, Florida, 2002.

* Boer C de. A Practical Guide to Splines revised edn. Springer: New York, 2001.

* Hastie T, Tibshirani R.. Generalized Additive Models. Chapman & Hall/CRC: New York, 1990.

@@

* Royston P, Sauerbrei W. Multivariable Model‐building. A Pragmatic Approach to Regression Analysis Based on Fractional Polynomials for Continuous Variables. Wiley: Chichester, 2008.

>>>>

* Harrell FE. Regression Modeling Strategies: With Applications to Linear Models, Logistic Regression, and Survival Analysis. Springer: New York, 2015. <br> *Integrates statistical rigor with practical guidance on variable selection, model specification, and validation across a range of regression contexts*.

* Royston P, Sauerbrei W. Multivariable model-building: a pragmatic approach to regression analysis based on fractional polynomials for modelling continuous variables. John Wiley & Sons; 2008. <br> *Presents a structured approach to modeling continuous variables using fractional polynomials, with an emphasis on reproducibility and clinical relevance*.

* Wood S. Generalized Additive Models. Chapman & Hall/CRC: New York, 2006. <br> *Offers an accessible yet thorough treatment of additive modeling techniques for capturing nonlinear relationships in multivariable settings*.

* Miller A. Subset Selection in Regression. Taylor & Francis: Boca Raton, Florida, 2002. <br> *Provides a critical examination of subset selection methods, discussing their statistical properties, limitations, and applications*.

* Boer C de. A Practical Guide to Splines revised edn. Springer: New York, 2001. <br> *Covers spline-based methods in detail, offering practical advice for incorporating flexible functional forms into regression models*.

* Hastie T, Tibshirani R.. Generalized Additive Models. Chapman & Hall/CRC: New York, 1990. <br> *Introduces foundational concepts in additive modeling, balancing statistical theory with illustrative applied examples*.

@@
